\subsection{Who is the customer, and how is our service of use to them?}

The customer, in our case, are people who travel, usually often and far. To be more precise, we can mention students as an important group of customers. Students often live far from their original home, and usually wish to visit their home town or family several times per year. We can, with relative certainty, say that students generally visit their family at least twice a year, in the break between the semesters. Often times, this number is larger. Three or four times is not unusual over the course of two semesters, or a school year, considering it is quite common to visit home during Easter, and usually some time during the fall semester.

Students generally have a quite restricted personal economy, which makes it important to find the cheapest way to travel. However, there are certain situations where travel time is more important than price. This is often the case for those who live far north, but study at a college or university in the southern half of Norway, but also in cases where the student studies in, say Trondheim, but lives south of Oslo or Bergen. In Northern Norway, the distance between towns are often large, and there might be fewer trains and buses. This makes travel times up to 12 hours quite common, and they can be even higher. In those cases, it might be worth it, even for a ``poor'' student, to pay the extra cost for a flight.

When it comes to the students who travel between cities in the southern half of Norway, the difference in travel times for various means of transportation is smaller, but they can still be very noticable. These differences can also vary between departures. The advantage students have when it comes to travel, is that they are often relatively free to choose when to depart, and usually have a bigger time frame where travel is possible. This makes our service very useful, but more on that later.

Another central group of customers are consultants and other advisors, travelling salesmen, and other people in similar situations, where their customers are spread out across the country, and their work requires them to physically seek them out. This group of people usually travel a lot, much more frequently than students, but the price is often less of an issue. In this case, travel time and a specific time of departure is commonly the most important. Additionally, it might be preferrable to have as few changes of transportation as possible.

Of the described customer groups, we place students who study a moderate distance from their home, as well as business travelers with a country wide customer base, in the category for people who will use the service frequently. This group of students are perhaps the ones that will find our service the most useful. Because their needs are shifting, it's practical to be able to sort based on various criteria, such as travel time and price. This lets the customer evaluate whether the difference in travel time is so major that paying extra for a flight (as opposed to train or bus) is worth it, or minor enough that they wish to save as much as possible by choosing the cheapest alternative. Alternatively, the customer can determine whether one of the service providers has particularly low priced tickets some time during the desired time frame for departure, and make a decision based on the information our service provides.

The business travelers will be able to simplify the process when they are traveling to a customer in a new location. Rather than seeking out the various transport service providers, they can specify the details of departure location and destination as well as desired departure time, and receive all relevant means of travel from various service providers or combinations of providers, with information about price, travel time and number of transport changes.

The category containing customers who will some times use our service, consists of the students who travel far, e.g. far north, or to Southern Norway from Mid- to Northern Norway. These customers will mainly find the price comparison feature between various flight providers most useful. If they need to change means of transport during the voyage, they can use our service to find the best departure. In this category, we also find the people who don't travel regularly. The service is useful when they are traveling to new places, in the same way the business travelers can utilize it when visiting customers in new locations. In this case, however, price again usually plays a bigger role. The third category, tourists, can also use the service in this same way.